My title

### 2024-11-04 paper/paper.qmd

## Objective
The survey aims to precisely capture voter intention and mood across important demographic and geographic divisions in order to predict the result of the US presidential election.

## Sampling Approach
* Stratified Random Sampling: To replicate the national electorate, stratify the sample according to age, gender, race/ethnicity, education level, urban/rural domicile, and area.

* Sample Size: Aim for a starting sample of five thousand people. This results in around 2000 to 2500 replies every wave, assuming a response rate of 40–50%.

## Respondent Recruitment
* Panel Providers: Partner with an online panel provider to find respondents that match each stratum’s specifications.Specify quotas to ensure that, for instance, you have 18% of respondents from the Midwest or 25% aging between 30 - 40.

* Random Sampling: Randomly select respondent within each strata.

* Incentives: To promote greater response rates and retention, provide a small monetary reward, such as $5 to $10 for each completed survey.

* Multi-Mode: To improve inclusivity and take into consideration differences in internet availability, use both phone and online surveys.

@@

## Essential Questions
* Are you currently registered to vote?
  - Yes
  - No

* Which state are you currently registered to vote in?
  (short answer)

@@

* Your gender idetification
  - Female
  - Male
  - Other

@@

* Which of the following best describes your racial background?
  - White or Caucasion
  - Black or African American
  - Hispanic
  - Asian or Pacific Islander
  - Native American
  - Other

>>>>

## Objective
The survey aims to capture voter intention and mood across important demographic and geographic divisions in order to predict the result of the US presidential election. This survey's methodology employs stratify sampling, effective respondent recruitment strategy and data validation techniques to ensure the accuracy of prediction.

## Sampling Approach
This survey employs Stratified Random Sampling, which involves divide the target population(In this case, the people who are eligible to vote in US) into subgroups(strata) based on their demographics characteristic. To simulate the national electorate, stratify the sample according to age, gender, race/ethnicity, education level, urban/rural domicile, and region. Also refer to the US Census data to determine the proportion of each strata, for example: if the census data shows there are 20% US citizen are between the age of 20 to 30, then there should be 20% of respondent in this age range. We aim for a starting sample of five thousand people since there were budget constraint.

## Respondent Recruitment
Partner with an online panel provider to find respondents that match each stratum’s specifications.Specify quotas to ensure that, for instance, you wish to have 18% of respondents from the Midwest or 25% aging between 30 - 40. Then randomly select respondent within each strata. To promote greater response rates and retention, provide a small monetary reward, such as $5 for each completed survey. To improve inclusivity and take into consideration differences in internet availability, use both phone and online surveys.

@@

## Budget Expenditure
* \$50k - \$60k for panel provider
* \$25k for incentives
* \$10k for Telephone survey services
* \$5k for data analysis

## Survey Structure
This survey will focus only on collecting participants' preferences for presidential candidates, not senate elections.Therefore, this survey only asks participants' choice of their favored presidential candidates. This design can make the entire questionnaire more simplify, while also collecting key data for predicting the presidential election.

Screener Section: Screening out people who are eligible to vote in each state. This can filter out participants who are not eligible to vote, thereby improving the accuracy of the prediction results.

* Are you currently registered to vote?
  - Yes
  - No

* Which state are you currently registered to vote in?
  - (Drop down box)

Presidential Ballot Section: Ask participants whether they would vote, who they would vote for, and how confident they are about that. This section can be used to find out the proportion of votes each candidate received among the participants.

@@

Demographics Section: This section collects detailed demographic characteristics of the participants to accurately predict the nation-wide election outcome.

* Your gender identification
  - Female
  - Male
  - Other

@@

* Which of the following best describes your race or ethnicity
  - White or Caucasian
  - Black or African American
  - Hispanic
  - Asian or Pacific Islander
  - Native American
  - Other
